%-------------------------
% Resume in LaTeX
% Author : Mehrdad Momeni Zadeh
% Optimized for: Backend & Distributed Systems Engineering Roles
% Use for: Amazon, Google, Uber, Lyft, Shopify, Meta, DoorDash, Most SWE positions
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for optimal space usage
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting - clean and ATS-friendly
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1   % ATS-friendly

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

% Tech line inside item list, no bullet
\newcommand{\resumeTech}[1]{\item[]\small{\textit{#1}}\vspace{-2pt}}

% Line spacing
\renewcommand{\baselinestretch}{1.1}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
  {\textbf{\Huge \scshape Mehrdad Momeni Zadeh}} \\ \vspace{8pt}
  \small
  \href{tel:+12365092543}{(236) 509-2543}
  $|$
  \href{mailto:mma236@sfu.ca}{mma236@sfu.ca}
  $|$
  \href{https://www.linkedin.com/in/mehrdad-momeni-zadeh-mma236}{LinkedIn}
  $|$
  \href{https://github.com/mehrdadmmz}{GitHub}
  $|$
  \href{https://www.mehrdad-mmz.com}{Portfolio}
  $|$
  Vancouver, BC
\end{center}

%----------- EDUCATION -----------
\vspace{-6pt}
\section{Education}
\vspace{2pt}
\resumeSubHeadingListStart
 \resumeSubheading
    {Simon Fraser University}{Burnaby, BC}
    {Bachelor of Science in Computer Science} {Expected May 2027}
    \resumeItemListStart
      \resumeItem{\textbf{GPA:} 3.4/4.33}
      \resumeItem{\textbf{Awards:} Dean's Honour Roll (Summer 2024, Summer 2025)}
      \resumeItem{\textbf{Relevant Coursework:} Distributed Systems, Database Systems, Data Structures \& Algorithms, Operating Systems, Software Engineering, Computer Networks, Object-Oriented Design}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- SKILLS -----------
\vspace{-3pt}
\section{Technical Skills}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
    \textbf{Languages:} Java, Python, Go, C++, TypeScript, SQL, Kotlin \\ \vspace{2pt}
    \textbf{Backend \& Web:} Spring Boot, Django, Express.js, React, Hibernate, REST APIs, gRPC, RabbitMQ \\ \vspace{2pt}
    \textbf{ML \& Data:} PyTorch, scikit-learn, NumPy, Pandas, PostgreSQL, MySQL, MongoDB \\ \vspace{2pt}
    \textbf{DevOps \& Tools:} Docker, Git, AWS (EC2, S3), GCP, CI/CD, Linux, JUnit, pytest, Mockito
  }}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\vspace{-3pt}
\section{Work Experience}
\vspace{2pt}
\resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant}{Burnaby, BC}
      {Simon Fraser University – DeLTA Lab\; {\scriptsize(\href{https://sites.google.com/view/sciml-fundemental-pde/home}{\color{blue}Project} | \href{https://github.com/mehrdadmmz/SciML-PDE}{\color{blue}Code})}} {Jan 2025 – Aug 2025}
    \resumeItemListStart
      \resumeItem{Developed and deployed ML training pipelines using Docker and GCP, reducing setup time by \textbf{40\%}.}
      \resumeItem{Implemented CI/CD workflows for a \textbf{6-person research team}, streamlining code integration processes.}
      \resumeItem{Optimized data preprocessing scripts in Python, improving model training speed by \textbf{2.5×} on large datasets.}
      \resumeItem{Collaborated with graduate students to design automated experiments using PyTorch and WandB.}
      \resumeItem{Co-authored research paper on neural network optimization accepted to \textbf{ICLR 2026} conference.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\vspace{-3pt}
\section{Technical Projects}
\vspace{2pt}
\resumeSubHeadingListStart

  % Event Hub - Backend platform
  \resumeProjectHeading
    {Event Hub — Full-stack event ticketing platform for university organizations}{\href{https://github.com/mehrdadmmz/StagePass}{\color{blue}GitHub}}
  \resumeItemListStart
    \resumeTech{Tech: Java, Spring Boot, TypeScript, PostgreSQL, Hibernate, React, JWT, REST APIs}
    \resumeItem{Deployed for campus events, managing \textbf{200+ student registrations} with automated confirmation emails.}
    \resumeItem{Implemented secure authentication using Spring Security with \textbf{JWT tokens} and role-based access control.}
    \resumeItem{Collaborated in a \textbf{team of 3} to design REST APIs and optimize database queries for faster load times.}
  \resumeItemListEnd

  % MicroGopher - Lead with distributed systems
  \resumeProjectHeading
    {Micro Gopher — Distributed task processing system using Go microservices}{\href{https://github.com/mehrdadmmz/MicroGopher}{\color{blue}GitHub}}
  \resumeItemListStart
    \resumeTech{Tech: Go, Docker, PostgreSQL, MongoDB, gRPC, RabbitMQ}
    \resumeItem{Refactored monolithic application into \textbf{4 Go microservices} improving fault isolation and scalability.}
    \resumeItem{Developed auth, logging, and notification services communicating via \textbf{gRPC} with message queuing.}
    \resumeItem{Containerized services with Docker, achieving \textbf{500+ requests/minute} throughput in load testing.}
  \resumeItemListEnd

    % ShareScreenly
  \resumeProjectHeading
    {ShareScreenly — Screen recording platform with instant video sharing}{\href{https://github.com/mehrdadmmz/ShareScreenly}{\color{blue}GitHub}}
  \resumeItemListStart
    \resumeTech{Tech: TypeScript, Express.js, Node.js, PostgreSQL, AWS S3, FFmpeg, Tailwind}
    \resumeItem{Scaled to \textbf{50+ active users} at SFU, reducing demo sharing time from \textbf{5 minutes to 2 minutes}.}
    \resumeItem{Integrated \textbf{FFmpeg} for video compression and \textbf{AWS S3} for scalable storage and delivery.}
    \resumeItem{Built PostgreSQL database with user authentication and role-based access for video management.}
  \resumeItemListEnd

  % NeuroDriver
  \resumeProjectHeading
    {Neuro Driver — AI-powered driving simulator with evolutionary learning}{\href{https://github.com/mehrdadmmz/NeuroDriver}{\color{blue}GitHub}}
  \resumeItemListStart
    \resumeTech{Tech: Python, PyGame, NumPy, Genetic Algorithms}
    \resumeItem{Trained neural network agents reducing collision rate by \textbf{35\%} over \textbf{50 generations} of evolution.}
    \resumeItem{Implemented fitness-based selection achieving \textbf{45\% improvement} in track completion rates.}
    \resumeItem{Created visualization dashboard displaying real-time neural network decisions and performance metrics.}
  \resumeItemListEnd


\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
